Prototype city generation for mobility simulation in urban typologies: a generalized framework

### 2017-12-21 manuscript/manuscript.tex
finalize od estimation procedure

\subsection{Estimation of origin-destination matrices}
There are three key

@@

\subsubsection{Initial estimates}
\begin{enumerate}
\item The zone-zone distance can be readily estimated by averaging the shortest-path distances for all unique OD pairings within a pair of zones. Given $P_{n_O n_D}$ as the shortest path for a given node-node OD pair, $n_On_D$, between two zones $O$ and $D$, then we can write
  \begin{equation}
    d_{OD} = \frac{\sum_{n_On_D \in V(O) \times V(D)}|| P_{n_On_D}||}{|V(O) \times V(D)|}
  \end{equation}
\item The road pricing cost can be zero for now, but these will be relevant for congestion pricing scenarios. Thus,
  \begin{equation}
    C^{rp}_{OD} = 0
  \end{equation}
\item Car in-vehicle time $CIVT$ can be computed using free-flow speeds $FFS_e$ along each edge $e$ of the shortest-path ODs for each zone pair to travel times, which are then averaged to obtain the final estimate:
  \begin{align}
    CIVT(P) &= \sum_{e \in P} \fr{||e||}{FFS_e}\\
    CIVT_{OD} &= \frac{\sum_{n_On_D \in V(O) \times V(D)} CIVT(P_{n_On_D})}{|V(O) \times V(D)|}
  \end{align}
\item Public transit in-vehicle time $PIVT$ is estimated using the procedure outlined in (iii) applied to the public transit graph
\item  Public transit access-egress 
\end{enumerate}

>>>>

\subsection{Estimation of origin-destination matrices}
There are three key inputs at the zonal level required for running SimMobility preday: zonal attribute data, skim matrices, and zone-zone travel time data.

@@

\subsubsection{Initial estimates}
\begin{enumerate}
\item The zone-zone distance can be readily estimated by averaging the shortest-path distances for all unique OD pairings within a pair of zones. Given $P_{n_O n_D}$ as the shortest path for a given node-node OD pair, $n_On_D$, between two zones $O$ and $D$, then we can write
  \begin{equation}
    d_{OD} = \frac{\sum_{n_On_D \in V(O) \times V(D)}|| P_{n_On_D}||}{|V(O) \times V(D)|}
  \end{equation}
\item The road pricing cost can be zero for now, but these will be relevant for congestion pricing scenarios. Thus,
  \begin{equation}
    C^{rp}_{OD} = 0
  \end{equation}
\item Car in-vehicle time $CIVT$ can be computed using free-flow speeds $FFS_e$ along each edge $e$ of the shortest-path ODs for each zone pair to travel times, which are then averaged to obtain the final estimate:
  \begin{align}
    CIVT(P) &= \sum_{e \in P} \fr{||e||}{FFS_e}\\
    CIVT_{OD} &= \frac{\sum_{n_On_D \in V(O) \times V(D)} CIVT(P_{n_On_D})}{|V(O) \times V(D)|}
  \end{align}
\item Public transit in-vehicle time $PIVT$ is estimated using the procedure outlined in (iii) applied to the public transit graph
\item Public transit access-egress times are obtained by averaging the shortest edges connecting each road node to a public transit node in zone $O$ and adding this to the corresponding value for zone $D$. We assume a walking speed of 5 km/h, and dividing the sum obtained by this value produces an estimate of the walking time for each zone $OD$ pair.

\item To estimate the public transit waiting time, we consider the median headway of the train/bus route on the first edge of all the shortest paths connecting public transit nodes in each zone-zone pairing. If there is a transfer on a given path, then the headway of the train/bus on the edge incident on the transfer point is added to the headway for the beginning of that path.

\item The public transit cost between zone $OD$s is taken as the average fare scaled by the relative average length of the shortest paths between the nodes in a given pair of zones.

\item We can compute the average number of transfers for each zone $OD$ by summing the number of transfers for the shortest paths in all node-node pairs between zones and dividing by the number of node-node pairings.
\end{enumerate}
